Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-30 phd/dissertation/chapter3.tex
begun work on Menger chapter
changes per discussion with G

\chapter{$W$ convergence and clustering games}

@@

\begin{proof}
  The forward implication shows that all $W$ spaces are first-countable spaces,
  and was proven in \cite{MR0413049}: if $\{U_n:n<\omega\}$ is a countable
  base at $x$, let $\sigma(n)=\bigcap_{m\leq n} U_m$. $\sigma$ is easily seen
  to be a winning predetermined strategy.

  If $X$ is not first countable at some $x$, let $\sigma$ be a
  predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
  an open neighborhood $U$ of $x$ which does not contain any
  $\bigcap_{m\leq n}\sigma(m)$ (otherwise
  $\{\bigcap_{m\leq n}\sigma(m):n<\omega\}$ would be a countable base at $x$).
  Let $x_n$ be an element of $\bigcap_{m\leq n}\sigma(m)\setminus U$ for all
  $n<\omega$. Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$
  for $\pl P$, so $\pl O$ lacks a winning predetermined strategy.
\end{proof}

@@

\begin{proof}
  Let $\sigma$ be a $k$-tactic for $\pl O$ in
  $\clusgame{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_1
          :
        s\in\alpha^{\leq k}
          \Rightarrow
        \oneptcomp\omega_1\setminus\sigma(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. Let $a_\sigma:\omega_1\to C_\sigma$ be an order
  isomorphism.

@@

  Finally, observe that the legal counterattack
    \[
      \<a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1),
        a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1),
        \dots\>
    \]
  has a range outside the open neighborhood
    \[
      \oneptcomp\omega_1
        \setminus
      \{a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1)\}
    \]
  of $\infty$. Thus $\sigma$ is not a winning $k$-tactic.
\end{proof}

@@

\begin{proof}
  Let $\sigma$ be a $k$-mark for $\pl O$ in
  $\clusgame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_2
          :
        s\in\alpha^{<\omega}
          \Rightarrow
        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. Let $a_\sigma:\omega_2\to C_\sigma$ be
  an order isomorphism.

  Choose $\beta_0<\dots<\beta_{k-1}<\omega_1$ such that for each $i<k$:
    \[
      a_\sigma(\beta_i)
        \in
      \bigcup_{n<\omega}
      \sigma(
        \<a_\sigma(\beta_0),\dots,a_\sigma(\beta_{i-1}),
          a_\sigma(\omega_1+i),\dots,a_\sigma(\omega_1+k-1)\>,
      n)
    \]

  Finally, observe that the legal counterattack
    \[
      \<a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1),
        a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1),
        \dots\>
    \]
  has a range outside the open neighborhood
    \[
      \oneptcomp\omega_2
        \setminus
      \{a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1)\}
    \]
  of $\infty$. Thus $\sigma$ is not a winning $k$-mark.
\end{proof}

@@

  In the case that $\cf\kappa=\omega$, let $\<\kappa_0,\kappa_1,\dots\>$ be
  an increasing sequence of cardinals limiting to $\kappa$. Then we define
  the coding strategy $\sigma$ for $\pl F$ as follows:
    \[
      \sigma(\emptyset) = \sigma_{K_0}(\emptyset)
    \]
    \[
      \sigma(\<F,C\>)
        =
      \bigcup_{n\leq|F|}
      \sigma_{\kappa_n}(\<F\cap \kappa_n,C\cap \kappa_n\>)
    \]

>>>>

\chapter{$W$ Convergence and Clustering Games}

@@

\begin{proof}
  The forward implication shows that all first-countable spaces are $W$ spaces,
  and was proven in \cite{MR0413049}: if $\{U_n:n<\omega\}$ is a countable
  base at $x$, let $\sigma(n)=\bigcap_{m\leq n} U_m$. $\sigma$ is easily seen
  to be a winning predetermined strategy.

  If $X$ is not first countable at some $x$, let $\sigma$ be a
  predetermined strategy for $\pl O$ in $\congame{X}{x}$. There exists
  an open neighborhood $U$ of $x$ which does not contain any
  $\bigcap_{m\leq n}\sigma(m)$ (otherwise
  $\{\bigcap_{m\leq n}\sigma(m):n<\omega\}$ would be a countable base at $x$).
  Let $x_n$ be an element of $\bigcap_{m\leq n}\sigma(m)\setminus U$ for all
  $n<\omega$. Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$
  for $\pl P$, so $\pl O$ lacks a winning predetermined strategy.
\end{proof}

@@

\begin{proof}
  Let $\sigma$ be a $k$-tactic for $\pl O$ in
  $\clusgamehard{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_1
          :
        s\in\alpha^{\leq k}
          \Rightarrow
        \oneptcomp\omega_1\setminus\sigma(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. Let $a_\sigma:\omega_1\to C_\sigma$ be an order
  isomorphism.

@@

  Finally, observe that the legal counterattack
    \[
      \<a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1),
        a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1),
        \dots\>
    \]
  has a range outside the open neighborhood %FIXME, say has finite range.
    \[
      \oneptcomp\omega_1
        \setminus
      \{a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1)\}
    \]
  of $\infty$. Thus $\sigma$ is not a winning $k$-tactic.
\end{proof}

@@

\begin{proof}
  Let $\sigma$ be a $k$-mark for $\pl O$ in
  $\clusgame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_2
          :
        s\in\alpha^{<\omega}
          \Rightarrow
        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. (Recall that $\mu_k$ is the
  $k$-Mark\"ov fog-of-war which turns perfect information into the last $k$
  moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be
  an order isomorphism.

  Choose $\beta_0<\dots<\beta_{k-1}<\omega_1$ such that for each $i<k$:
    \[
      a_\sigma(\beta_i)
        \in
      \bigcap_{n<\omega}
      \sigma(
        \<a_\sigma(\beta_0),\dots,a_\sigma(\beta_{i-1}),
          a_\sigma(\omega_1+i),\dots,a_\sigma(\omega_1+k-1)\>,
      n)
    \]

  Finally, observe that the legal counterattack
    \[
      \<a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1),
        a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1),
        \dots\>
    \]
  has a range outside the open neighborhood %FIXME, say has finite range.
    \[
      \oneptcomp\omega_2
        \setminus
      \{a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1)\}
    \]
  of $\infty$. Thus $\sigma$ is not a winning $k$-mark.
\end{proof}

@@

  In the case that $\cf\kappa=\omega$, let $\<\kappa_0,\kappa_1,\dots\>$ be
  an increasing sequence of cardinals limiting to $\kappa$. Then we define
  the coding strategy $\sigma$ for $\pl F$ as follows:
    \[
      \sigma(\emptyset) = \sigma_{\kappa_0}(\emptyset)
    \]
    \[
      \sigma(\<F,C\>)
        =
      \bigcup_{n\leq|F|}
      \sigma_{\kappa_n}(\<F\cap \kappa_n,C\cap \kappa_n\>)
    \]
